Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
expl:heatmap, sim vel,

4.  [Scatter plots]{.underline}: Scatter plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.

```{python}
def scatter_plot(x, y, xerr = None, yerr = None, sigma = False):
    """
    Generates a scatter plot of two datasets with optional error bars, fits a linear model to the data, 
    and displays the fitted line on the plot.

@@

Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers whith $sigma > 3$

-   Histograms

-   Deviation

@@

::: panel-tabset
## Right Ascnsion

@@

# Create a pair grid
sns.pairplot(vel_data, corner=True)
plt.show()
```

## Heatmap
```{python}
# Compute the correlation matrix
corr_matrix = vel_data.corr()

@@

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```

@@

scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```
:::
## Absorbsion

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:-----------------:|:----------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

```{python}
scatter_plot(dt["AB"], dt["AG"])#, scatter_plot(dt["AB_int"], dt["AI"])
```

>>>>

4.  [Plots]{.underline}: Plots are essential for visually assessing the relationship between two datasets, identifying correlations, trends, and outliers, and evaluating the fit of linear models.

```{python}
def scatter_plot(x, y, xerr = None, yerr = None, sigma = False, logscale = False):
    """
    Generates a scatter plot of two datasets with optional error bars, fits a linear model to the data, 
    and displays the fitted line on the plot.

@@

Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $sigma > 3$

- Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix. It’s like a color chart that shows us how closely related different variables are.

In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them. The color of each cell represents the strength and direction of the correlation, with darker colors indicating stronger correlations.

- Histograms: Because not all of our data have the same number of counts, the comparison with histograms between data that are not the same, doesn't help us right now.[^3] This is why we will only use histograms for comparing the distribution of same-data columns normalized by their maximum value

[^3]: When we will use the outer join table we could use histograms due to the large number of counts.

@@

::: panel-tabset
## Right Ascension

@@

# Create a pair grid
sns.pairplot(vel_data, corner=True)
plt.show()
```
[?] The close correlation between all of the velocities, could be due to the fact that all of them measure the velocity of each galaxy, but from a different frame of reference.
## Heatmap
```{python}
# Compute the correlation matrix
corr_matrix = vel_data.corr()

@@

```{python}
scatter_plot(dt["a26_1"], dt["R1"], logscale = True)
```

@@

scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```
:::
## Absorpsion

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:-----------------:|:----------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrinsic B band extinction/absorption |              0               |

```{python}
scatter_plot(dt["AB"], dt["AG"], logscale = True)#, scatter_plot(dt["AB_int"], dt["AI"])
```
